### 2024-10-31 manuscript.tex
Add co-authors

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\usepackage{lineno}
\linenumbers
\setsansfont{Source Sans Pro}
\setmainfont{EB Garamond}
\setmonofont[Scale=0.8]{SpaceMono}[
	Path=./fonts/,
	Extension=.ttf,
	UprightFont=*-Regular,
	BoldFont=*-Bold,
	ItalicFont=*-Italic,
	BoldItalicFont=*-BoldItalic
]
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, Graeme Plank, Sean Hartery, Simon Parsons, Simon P. Alexander, Alex J. Schuddeboom, …}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titlespacing*{\subsection}{0pt}{13pt}{4pt}
\parskip=6pt
\parindent=0pt

@@

\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,}$*, Frida A.-M. Bender$^\mathsf{1}$, Adrian J. McDonald$^\mathsf{2}$, Graeme Plank$^\mathsf{2}$, Sean Hartery$^\mathsf{3}$, Simon Parsons$^\mathsf{4}$, Simon P. Alexander$^\mathsf{5}$, Alex J. Schuddeboom$^\mathsf{2}$, \ldots\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU) and Bolin Centre for Climate Research, Stockholm University, Stockholm SE-106 91, Sweden\\
$^\mathsf{2}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\
$^\mathsf{3}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
$^\mathsf{4}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
$^\mathsf{5}$Australian Antarctic Division, Kingston, Tasmania, Australia; Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large \today\\[0.4cm]

@@

The authors have made the following contributions based on the CRediT taxonomy
(\url{https://credit.niso.org}).  PK: conceptualization, data curation, formal
analysis, investigation, methodology, software, writing – original draft; FB:
conceptualization, funding acquisition, project administration, supervision,
and writing – review \& editing; AM: data curation, investigation, resources,
writing – review \& editing. [TODO]

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\usepackage{lineno}
\linenumbers
\setsansfont{Source Sans Pro}
\setmainfont{EB Garamond}
\setmonofont[Scale=0.8]{SpaceMono}[
	Path=./fonts/,
	Extension=.ttf,
	UprightFont=*-Regular,
	BoldFont=*-Bold,
	ItalicFont=*-Italic,
	BoldItalicFont=*-BoldItalic
]
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, Adrian J. McDonald, Graeme Plank, Sean Hartery, Simon Parsons, Simon P. Alexander, Greg M. McFarquhar, John J. Cassano, Alex J. Schuddeboom, …}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titlespacing*{\subsection}{0pt}{13pt}{4pt}
\parskip=6pt
\parindent=0pt

@@

\begin{center} \Large \sffamily\textbf{Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON and the ERA5 and MERRA-2 reanalyses}\\[0.4cm]
\large Peter Kuma$^\mathsf{1,2}$*, Frida A.-M. Bender$^\mathsf{1,2}$, Adrian J. McDonald$^\mathsf{3}$, Graeme Plank$^\mathsf{3}$, Sean Hartery$^\mathsf{4}$, Simon Parsons$^\mathsf{5}$, Simon P. Alexander$^\mathsf{6,7}$, Greg M. McFarquhar$^\mathsf{8}$, John J. Cassano$^\mathsf{9,10,11}$, Alex J. Schuddeboom$^\mathsf{3}$, \ldots\\[0.4cm]
\small
$^\mathsf{1}$Department of Meteorology (MISU), Stockholm University, Stockholm,, Sweden\\
$^\mathsf{2}$Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden\\
$^\mathsf{3}$School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand\\
$^\mathsf{4}$Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada\\
$^\mathsf{5}$New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia\\
$^\mathsf{6}$Australian Antarctic Division, Kingston, Tasmania, Australia\\
$^\mathsf{7}$Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia\\
$^\mathsf{8}$Cooperative Institute for Mesoscale Meteorological Studies, and School of Meteorology, University of Oklahoma, Norman, Oklahoma, USA\\
$^\mathsf{9}$Department of Atmospheric and Oceanic Sciences, University of Colorado Boulder, Boulder, Colorado, USA\\
$^\mathsf{10}$National Snow and Ice Data Center, University of Colorado Boulder, Boulder, Colorado, USA\\
$^\mathsf{11}$Department of Atmospheric and Oceanic Sciences, University of Colorado Boulder, Boulder, Colorado, USA\\[0.2cm]
*Corresponding author: Peter Kuma (\href{mailto:peter.kuma@misu.su.se}{peter.kuma@misu.su.se})\\[0.4cm]
\large \today\\[0.4cm]

@@

The authors have made the following contributions based on the CRediT taxonomy
(\url{https://credit.niso.org}).  PK: conceptualization, data curation, formal
analysis, investigation, methodology, software, writing – original draft; FB:
conceptualization, funding acquisition, project administration, supervision,
and writing – review \& editing; AM, GP, SH, SP, SA, GM, JC, and AS: data
curation, investigation, resources, writing – review \& editing; [TODO]
